Assessing Usability of Tor Browser

### 2015-04-10 PETS2015-paper/paper.tex
new PETS template
new sections

\documentclass{acm_proc_article-sp}
\usepackage{color}
\usepackage[hyphens]{url}
\usepackage{longtable}
\usepackage{graphicx}
\usepackage{enumitem}
\usepackage{pdfpages}

@@

\begin{document}
\input{tex-inputs/title.tex}
\input{tex-inputs/abstract.tex}
\input{tex-inputs/introduction.tex}
\input{tex-inputs/related_work.tex} 
\input{tex-inputs/experiment.tex}
\input{tex-inputs/conclusion.tex}

>>>>

\documentclass{sig-alternate-hotpets15}
\usepackage{color}
\usepackage[hyphens]{url}
\usepackage{longtable}
\usepackage{graphicx}
\usepackage{enumitem}
\usepackage{pdfpages}

@@

\begin{document}

\title{Assessing Usability of Tor Browser}
\numberofauthors{1}
\author{
 \alignauthor David Fifield\textsuperscript{1} and Linda N. Lee\textsuperscript{1}, Serge Egelman\textsuperscript{1,2}, David Wagner\textsuperscript{1}\\
   \vspace{0.5em}
   \affaddr{\textsuperscript{1}University of California, Berkeley, \{fifield,lnl,egelman,daw\}@cs.berkeley.edu}, \\
   \affaddr{\textsuperscript{2}International Computer Science Institute, egelman@icsi.berkeley.edu}\\
}

%\numberofauthors{1}
%\author{
% \alignauthor Anonymous\\
%   \vspace{0.5em}
%   \affaddr{Some Place}
%}
\maketitle
{\color {red} TODO: write the paper for PETS currently, it is the same as the class paper..}

\begin{abstract}
Abstract here.
\end{abstract}

% A category with the (minimum) three required fields
%\category{K.6.5.}{Management of Computing and Information Systems}{Security and protection}[Unauthorized access]

%\terms{Human Factors}{Measurement}{Security}

\keywords{Privacy, Security, User Studies, Anonymity, Tor} % NOT required for Proceedings

\section{What we already did/background stuff}

Text here.

\section{Design}
In this section, we outline previous research regarding how users understand and act on the Internet, communicating relevant risks to users, and usability of Tor Browser

\section{What we want feedback on}
